---
title: "Run simulated data with multiple endpoints"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
devtools::load_all()
```

```{r setup}
library(Permeate)
library(ggplot2)
library(gtable)
```

## Set working directory
```{r}
dir<- "~/Documents/"
```

## Choose setting: 1) choose pre-specified settings ("setting1","setting2","setting3") or 2) choose  "custom" and specify your own setting, i.e. specify N.sim,N.outcomes,RR,prop.outcome,N1,N2

### setting 1 corresponds to  N.sim=10000,N.outcomes=3,RR=c(0.60,0.60,0.70),prop.outcome=c(0.22,0.20,0.12),N1=200,N2=200)
### setting 2 corresponds to N.sim=10000,N.outcomes=3,RR=c(0.25,0.4,0.6),prop.outcome=c(.05,.02,.03),N1=496,N2=994)
### setting 3 corresponds to N.sim=10000,N.outcomes=3,RR=c(0.60,0.55,0.5),prop.outcome=c(.02,.04,.01),N1=1430,N2=2765)
```{r}
#options(future.globals.maxSize = 1000 * 1024^8) ## Uncomment this line if memory issues
setting_name="setting3"
```

## Run main function for different correlation values
```{r}
cor_l <- c(0.80,0.60,0.40,0.20,0.01) ## set correlation intervals
for(i in 1:length(cor_l)) {
  print(i)
  result<-main_run(setting_name,corr=cor_l[i],dir)
}
```






