---
title: "Run simulated data with multiple endpoints"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
devtools::load_all()
```

```{r setup}
library(Permeate)
```

## Set working directory
```{r}
dir<- "~/Documents/"
```

## Choose setting: 1) choose pre-specified settings ("setting1","setting2","setting3") or 2) choose  "custom" and specify your own setting, i.e. specify N.sim,N.outcomes,RR,prop.outcome,N1,N2

### setting 1 corresponds to  N.sim=10000,N.outcomes=3,RR=c(0.60,0.60,0.70),prop.outcome=c(0.22,0.20,0.12),N1=200,N2=200)
### setting 2 corresponds to N.sim=10000,N.outcomes=3,RR=c(0.25,0.4,0.6),prop.outcome=c(.05,.02,.03),N1=496,N2=994)
### setting 3 corresponds to N.sim=10000,N.outcomes=3,RR=c(0.60,0.55,0.5),prop.outcome=c(.02,.04,.01),N1=1430,N2=2765)
```{r}
#options(future.globals.maxSize = 1000 * 1024^8) ## Uncomment this line if memory issues
setting_name="setting3"
```

## Run main function for different correlation values
```{r}
cor_l <- c(0.80,0.60,0.40,0.20,0.01) ## set correlation intervals
for(i in 1:length(cor_l)) {
  print(i)
  result<-main_run(setting_name,corr=cor_l[i],dir)
}
```

## Load results for plotting
## Specify pattern based on setting
```{r}
result1 <- load_result(pattern=setting_name,path=dir)
power1.df<-result1$power.df
power1.df$cor <- rep(c(.01,.20,.40,.60,.80),times=length(unique(power1.df$model)))
power1.df <- arrange(power1.df,cor)
typeone1.df<-result1$typeone.df
typeone1.df$cor <- rep(c(.01,.20,.40,.60,.80),times=length(unique(typeone1.df$model)))
typeone1.df <- arrange(typeone1.df,cor)
## Load function setting 
setting<-set_setting(setting_name)
```

## Plots
```{r}
pd <- position_dodge(0.3)
g <- list()
g[[1]]<-ggplot(power1.df, aes(x=factor(cor),y=estimate,colour=model,group=model)) +
  geom_point(aes(shape = model, color =model),position=pd)+
  geom_errorbar(aes(ymin=lower,ymax=upper),width=0.0,position=pd)+
  theme_classic()+
  #theme(plot.margin=unit(c(0,0,0,1),"cm"))+
  coord_cartesian(ylim=c(60,100))+
  #ggtitle(paste0("RR=(",setting$RR,");",TeX("$\\beta_{0}$:"),setting$prop.outcome,TeX("; $X_{c}$="),setting$N1,TeX("$X_{t}$="),setting$N2))+
  theme(plot.title = element_text(size = 10),axis.text.y = element_text(size = 8),axis.text.x = element_text(size = 8),axis.title.y=element_text(size = 8))+
  labs( tag = "A") +
  ylab("Power")+
  xlab("")

g[[2]]<-ggplot(typeone1.df, aes(x=factor(cor),y=estimate,colour=model,group=model)) +
  geom_point(aes(shape = model, color =model),position=pd)+
  geom_errorbar(aes(ymin=lower,ymax=upper),width=0.0,position=pd)+
  theme_classic()+
  geom_hline(yintercept=5,color="gray",linetype="dashed")+theme_classic()+
  coord_cartesian(ylim=c(0,10))+
  #theme(plot.margin=unit(c(0,0,0,1),"cm"))+
  labs( tag = "B") +
  #ggtitle(TeX("RR=(0.6, 0.6, 0.7); $\\beta_{0}$=(0.22,0.20,0.12); $X_{c}=X_{t}=200$"))+
  theme(plot.title = element_text(size = 10),axis.text.y = element_text(size = 8),axis.text.x = element_text(size = 8),axis.title.y=element_text(size = 8))+
  ylab("Type I error")+
  xlab("")
legend = gtable_filter(ggplotGrob(g[[1]]), "guide-box") 
gsave<- grid.arrange(arrangeGrob(g[[1]] + theme(legend.position="none"), 
                                 g[[2]] + theme(legend.position="none"), 
                                 ncol=2,nrow=1,
                                 bottom = textGrob("Correlation", rot = 0, vjust=1,hjust=0.0,y=1.8,x=0.45)),legend,heights=0.5,
                     widths=c(8,1),nrow=1)
width = 10
height = 4#(9/16) * width
ggsave(paste0("./",setting_name,".jpeg"),width=width,height=height,dpi=300,gsave)
```




